The goal of this chapter is to give a clear idea of why the project was needed,
who is impacted by the project and how it stands in relation to other projects.
First, we look at user story.
Secondly, we consider three cases of other companies that have solved
a similar problem and explain how they relate to our own project. % add links to relevant parts
Then we describe the stakeholders and assess the ethical implications of our project.
Finally, we take a look at some potential bottlenecks we could have run into.


\section{Problem statement}\label{sec:problem-statement}
During our first meeting with Mr. Kahawati from Avonic, we have identified the problem statement as follows:

Avonic would like to make it easier to record educational sessions by creating
a camera that follows the speaker as they move around in a room. The way they want to do
this is by using a camera at the back of the room that automatically tracks the speaker.
Avonic has already tried to do this using just the visual information of the camera, but
it turned out not to be enough to accurately track speakers in all cases:
multiple people may look like the speaker by moving or opening their mouths,
while only one person is actually speaking.

To solve this problem, Avonic wants to try to use a microphone in addition
to the camera to identify the speaker. A common setup would be to have
the camera in the back of the room and the microphone in the front above the speaker(s).
In order to explore this solution, Avonic has asked us to spend
ten weeks working on a system that tracks a speaker using both a camera and a
microphone. The camera we have to use is the Avonic CM70 model and the
microphone is the Sennheiser TeamConnect Ceiling 2. We are not allowed to
reprogram these devices. That is why a single-board computer, the Nvidia Jetson Nano,
has to be used to communicate with the camera and microphone through application programming
interfaces (APIs). Moreover, it should be easy for a user to start the system
and it should not require any technical knowledge.

To recap:
using the camera, microphone and single-board computer mentioned above,
we had to find a way to automatically move to camera to point at a speaker after minimal installation.

\section{Available solutions}\label{sec:available-solutions}
We now discuss three different solutions that are already available for
customers. These products were created by companies other than Avonic to solve
a similar problem to the one described in
\hyperref[sec:problem-statement]{Section 2.1}. Looking at such products helps to get a
better idea of the state of the art. For every case below, we contrast the
solution with Avonic’s vision and explain how it relates to the project we
worked on.

\paragraph{AVer}\mbox{} \\
AVer created a camera that can ``automatically track a presenter’s face and
movements''\cite{aver-camera}. The camera stands alone and is not helped by an
external microphone. Instead, it has a so-called ``dual-lens design'' that
allows to keep a secondary panorama view while zooming in on the speaker. In
this way, new speakers can still be recognized when they are not recorded by
the zoomed in lens.

Though Avonic has tried to use a dual-lens design before, our project is about
using a single camera with a single lens. To make up for the lack of multiple
lenses, we have to use a microphone. This way it is still possible to detect
new speakers that are not in view of the camera. The video processing
techniques used by AVer may be similar to the ones employed by Avonic, but
since the microphone was an essential part of our project, the AVer camera
could not serve as a good source of inspiration.

\paragraph{Yealink}\mbox{} \\
On top of a dual-lens design similar to the one AVer used, the Yealink camera
has a built-in microphone array which helps to localize the sound and track the
speaker\cite{yealink-camera}. As audio from a microphone array is used to
detect the speaker's location, this is similar to our project.

The big difference is that the Yealink microphone is built into the camera,
which eliminates the need to translate data from the microphone to the camera.
Since we have a seperate microphone at a different position from the camera, we
face an entirely different problem from Yealink.

\paragraph{Cisco}\mbox{} \\
Using one camera, Cisco locates the speaker and zooms in on that speaker, while
another camera is watching the entire room to look for the next
speaker\cite{cisco-camera}. This dual-camera approach helps to switch quickly
between different speakers. It can be compared to the dual-lens design used by
AVer and Yealink; all these products have an option to search for a new speaker
while recording the active speaker.

The use of two cameras thus makes it easier for Cisco to localize the speaker.
The overall problem is in this way made less complex. Avonic wants to use only
one camera and one microphone and try to track speakers as well as companies
like Cisco do with two or more cameras.


As we can see, the most common approach to the speaker localization problem is
to use a dual-lens or dual-camera design. On behalf of Avonic, we experimented
with a new approach: one camera and one microphone. This poses new problems.
Our devised solution is described in \hyperref[ch:solution]{Chapter 4}.

\section{Stakeholders}\label{sec:stakeholders}
This section describes who the stakeholders of our project are and how we considered their interests during the ten week process. The
definition of stakeholder that we are going to use is as follows: “All those who have an interest in the system and who will eventually be
responsible for its acceptance”\cite{stakeholder-definition}.
Using this definition, we identified three main types of stakeholders. These people are directly affected by the result of our project.
The types of stakeholders of our project are as follows:

\paragraph{Clients}\mbox{} \\
Potential clients of Avonic who are going to make use of our software in the future. This includes university staff or conference
organizers. Anyone who buys the Avonic camera for personal use falls into this category. It is important to these clients that the camera
tracks speakers accurately and that it is easy to install.
\paragraph{Developers}\mbox{} \\
Developers who are going to be building upon our code in the future. Since we write our code for Avonic, we expect this category to include
only their developers. It is important to the developers that the code is well written and well documented. Some of the criteria we
use to determine whether code is well written are test coverage, readability and extensibility. These criteria and more are explained in
\hyperref[ch:workflow-and-teamwork]{Chapter 5} where we talk about the workflow.
\paragraph{Avonic}\mbox{} \\
Avonic as a company influences the requirements of our project. They have the general picture in mind, considering both the clients and
the developers. It is important to them that the compromises made in the process are carefully considered and explained. This includes a
clear and elaborate report that explains precisely what steps have been taken to reach the conclusion. Such a report can be used by Avonic
to decide whether the experiment is worth doing again.

\paragraph{Satisfaction of all stakeholders}\mbox{} \\
In order to satisfy every stakeholder as much as possible, we continually talked to people from Avonic. We had weekly meetings with Ali
Kahawati, one of the software developers at the company, and visited the office three times a week to be able to talk with other employees as well.
Throughout the project, this helped to stay in touch with the wants of the stakeholders. We had no direct contact with the clients, so this
group was mainly represented by the Avonic team.


\section{Possible pitfalls}\label{sec:possible-pitfalls}
At the start of the project, we identified two possible risks which we needed to decide on how to avert.
As these risks threatened to slow down our progress, we tried to reduce their impact as much as possible.
Below are the issues listed in order of severity.
\subsection{Access to hardware}
The largest risk was access to the hardware (or lack thereof). Since our
project relies on the availability of both the camera and microphone, we would
have been unable to work on it without them. The contact person from Avonic --
Mr. Kahawati -- informed us that we would only be able to come to the office
three days a week, which would have prevented us from working on the project
sometimes.

We were allowed to bring a camera home to test, but that was not an option with
the expensive and large ceiling microphone. We mitigated this by using a
virtual private network (VPN) connection to the office. This way we had a way
to access the microphone remotely, although we could not test it very well when
nobody from the group was at the office.

Apart from the camera, we also needed an NVIDIA Jetson Nano to run our software.
This device became available during the eighth week of the project, which caused
some new problems to appear in our code. Up untill that point we had used our own
computers to simulate the production environment. Despite the risk of having
too little time to fix new bugs, the last two weeks turned out to be enough to
make everything work on the Jetson Nano.

\subsection{Work space}
During the project we could visit the office at most three days a week. This meant that we did not always have a place to work together as a
group. Group meetings required a quiet meeting room, which we were not always able to find.
On the days that we were not able to go to the office, we tried to find a room on the TU Delft campus. Whenever we were not able to get a
meeting room, we went to a public place on campus. In such places, we could still have meetings and we could still work closely together.
All our meetings with Mr. Kahawati happened on days we could visit the office, so those meetings did not suffer from our limited time at the office.

\section{Ethical implications}
For our project, we are going to make use of video and audio; both can be considered personal data.
Since personal data can be used with malicious intent, we are cautious and thoughtful with regard to the ethics of the system.
The ethical implications of the system should be carefully reviewed to disallow any unethical abuse of the system.
Below we cover five important topics related to ethical use of personal data to give more insight into our system and its potential use cases.
\subsection*{Processing of personal data}
Our project revolves around working with a microphone and a camera.
Both of these process personal data in the forms of audio and video and transmit this so that it can be used by people.
Our system does not use any personal part of the data because we only utilize the location information from the speaker.
Therefore, our system does not, in and of itself, process any personal data, but the hardware that we use together with the system does.
For instance, the microphone, made in Germany by Sennheiser, processes audio from the room.


We can not modify the camera or microphone (or otherwise alter their behavior), but what we can do to mitigate the ethical risks of our
project is to ensure we do not use the transmitted personal information ourselves
\subsection*{Profiling or systematic monitoring}
Our tools (a camera and a microphone, conceptually) could technically be used in the surveillance of a room of people who have not consented to have video taken of them.
We have access to the video camera stream, but we are not planning to store anything on the device after processing it locally.
Our software alone therefore cannot be used to profile or monitor individuals.
A person who has access to the microphone and the video stream is able to more accurately identify the speaking person and afterward store this information.
Those ethical implications do not fall on us as the developers in this scenario.
\subsection*{Processing of previously collected data}
We do not have access and are not allowed to use any of the data stored by Avonic.
The system has been extended with visual tracking that required data from previously recorded people, but that data was sourced from publicly available, previously trained models.
Apart from the visual tracking feature, there is no part of our system which requires previously stored data.
\subsection*{Exporting to non-EU countries}
As explained above, the microphone and camera that we are using can be used to send personal data to any place in the world.
This data involves video and audio of people.
We can prevent the data obtained from going abroad by limiting the traffic from the network.
\subsection*{Importing of personal data}
We do not plan on importing personal data from anywhere.
We do not personally need the data obtained using the microphone and camera, so we will surely not import any data from non-EU countries.
Users of the cameras and microphones can use those devices to create personal data and send it abroad, but they could use any camera to do
this, and it does not pose any ethical risks besides the ones explained in \hyperref[]{section 2.4.2}. % TODO
