In this chapter we reflect on both the process and the result of our project.
When we discuss the process, we focus on things that could have been done
better by our team in terms of practices.
When we discuss technological improvements, we focus on what can be changed in
order to improve the overall performance of our tracker.

\section{Process reflection}
Many things went well in the process of creating the speaker tracker. However,
there are two points of improvement that we want to reflect on. We also
highlight our testing practice because of how helpful it was during the
entirety of the project.

\paragraph{Production server} \mbox{} \\
As discussed in \hyperref[subsection:breaking-production-server]{section 5.5.2}
we had some problems with the production server. This was because we were
sometimes using the development server to test our code without realizing that
it works fundamentally differently from the production server. The production
server uses multiprocessing, while the development server does not. This caused
problems with sharing data between threads.
After encountering this issue, we started using the production server for
everything. If we had done so from the start, we could have avoided many issues
related to multithreading.

\paragraph{Access to SBC} \mbox{} \\
It took eight weeks until we got access to the NVIDIA Jetson. This meant that we
had only slightly more than one week left to fix the issues that arose from deploying
our software on the SBC for the first time. For access to the NVIDIA Jetson, we
had to wait on Avonic to provide us with one. Therefore, the problem was mostly
out of our control.
If we had had access to the SBC at an earlier stage of the project, any bugs
related to the SBC would have been caught and hopefully ironed out.

\paragraph{Testing} \mbox{} \\
Throughout the project, we always tested our code before merging into the main
branch on GitLab. We were dedicated to keeping the test coverage above 80\%.
This high coverage helped us to make sure no other functionality was broken when
new functionality was added. Many bugs have been caught this way before they
were merged.

\section{Technological improvements}
If Avonic wants to continue to work on our tracker, we would advise them to
focus on two improvements. Both of them are related to the quality of the video
stream. In this section we discuss how these changes would help to improve
our speaker tracker.

\paragraph{Dependency injection} \mbox{} \\
As described in subsection \ref{subsection:solution_webui} on the web UI,
we struggled with dependency injection for our Flask application.
In the next iteration of the project, this problem should be addressed 
by a different choice of the framework for the web UI or by a proper
implementation of dependency injection.

\paragraph{Tracking with adaptive zoom} \mbox{} \\
The audio model described in \hyperref[subsection:tracking]{section 4.5.3} uses
adaptive zooming. However, the constant zooming may not pleasant to look at.
Sometimes the speaker goes out of view, because the zooming increases the impact
of inaccurate microphone directions. Even when the speaker stays in view, the
zooming may be distracting to the viewers, because it can happen too fast and
too often.
For future improvements of the audio model, we would suggest to make the zoom
speed depend on the speed of its change. Another way to improve the adaptive
zooming would be to change the zoom less often. This would make the video stream
more pleasant to watch.

\paragraph{Porting YOLO} \mbox{} \\
When discussing object detecting models with Avonic, we discovered that they use an
in-house version of YOLO ported to TensorRT\footnote{\url{https://developer.nvidia.com/tensorrt}}, which allows for better performance
of the model. This would reduce the load of the system, allowing for more features,
and deployment on platforms with less powerful hardware.
